---
title: "Project 2-3"
author: "Benson Toi and Jay Lee"
date: "3/10/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r lib}

library(tidyverse)
library(stringr)

```

## Ramen

This Data Set had 2580 reviews on the Ramen noodles from The Ramen Rater's "The Big List." I want to know which brand, favor, Ramen's style, brand's origin based on the rating by the reviewer. 

```{r ds}
Ramen_DS <- read.csv(file="https://raw.githubusercontent.com/Benson90/Project2/main/ramen-ratings.csv",header = TRUE, sep=",")

```


## Data Transformation 

We were removing some unrated data and converting the character to Numbers. 

```{r Transformation}

#remove unrated data
Ramen_DS <- Ramen_DS[!(Ramen_DS$Stars=="Unrated"),]

#convert from char to number
Ramen_DS$Stars <-as.numeric(Ramen_DS$Stars)

head(Ramen_DS)

```

## Cleaning the insufficient review data

Grouping the category and using the data had a minimum of 50 or 10 reviewers. 

```{r filter}

#Filter out the number of review less than 50 or 10
#Country
Country_counts <- Ramen_DS %>%
    group_by(Country) %>%
    tally

Frequent_country <-  Country_counts %>%
    filter(n >= 50) %>%
    select(Country)

#Style
Style_counts <- Ramen_DS %>%
    group_by(Style) %>%
    tally

Frequent_Style <-  Style_counts %>%
    filter(n >= 50) %>%
    select(Style)

#Brand
Brand_counts <- Ramen_DS %>%
    group_by(Brand) %>%
    tally

Frequent_Brand <-  Brand_counts %>%
    filter(n >= 50) %>%
    select(Brand)

```

## Found the Top favorite Ramen based on Brand, Style, and Country

By using the sort function and calculating the mean review rate to find the top review from the reviewer.

```{r sort}

Ranking_DS <- Ramen_DS %>%
  group_by(Country) %>%
  filter(Country %in% Frequent_country$Country) %>%
  summarize(mean_rate = mean(Stars)) %>%
  arrange(desc(mean_rate))
head(Ranking_DS,10)

Ranking_DS <- Ramen_DS %>%
  group_by(Style) %>%
  filter(Style %in% Frequent_Style$Style) %>%
  summarize(mean_rate = mean(Stars)) %>%
  arrange(desc(mean_rate))
head(Ranking_DS,10)

Ranking_DS <- Ramen_DS %>%
  group_by(Brand) %>%
  filter(Brand %in% Frequent_Brand$Brand) %>%
  summarize(mean_rate = mean(Stars)) %>%
  arrange(desc(mean_rate))
head(Ranking_DS,10)

```
## Summary

We found that the reviewer likes Asia-made Ramen. And Reviewer favorite's style is Ramen in Pack, but the rating difference is in the close gap. Also, the Top 5 favorite brand from a reviewer is Indomie, Samyang Foods, Paldo, Nongshim, and Nissin.
Since we are staying in the US, we would like to know what this US-made favorite is.  And get to know the top-rating variety of Ramen. 

```{r more}

US_Top_DS <- Ramen_DS %>%
  filter(Country =="USA") %>%
  arrange(desc(Stars))

head(US_Top_DS,10)

Style_Top_DS <- Ramen_DS %>%
  filter(Style =="Pack") %>%
  arrange(desc(Stars))

head(Style_Top_DS,10)

Brand_Top_DS <- Ramen_DS %>%
  filter(Brand =="Indomie") %>%
  arrange(desc(Stars))

head(Brand_Top_DS,5)

Brand_Top_DS <- Ramen_DS %>%
  filter(Brand =="Samyang Foods") %>%
  arrange(desc(Stars))

head(Brand_Top_DS,5)
```


